Bibat: Batteries-include Bayesian Analysis Template

### 2024-04-10 paper/main.qmd
Mention lovelyplots in paper

Bibat integrates many widely-adopted open-source tools to implement
the components of a Bayesian workflow. These include pydantic
[@pydanticdevelopersPydantic2022] and pandera [@niels_bantilan-proc-scipy-2020]
for data modelling, Stan [@carpenterStanProbabilisticProgramming2017] for
statistical inference, cmdstanpy [@standevelopmentteamCmdStanPy2022] for
python-Stan interface, arviz [@kumarArviZUnifiedLibrary2019] for storing and
analysing inferences and sphinx [@georgbrandlandthesphinxteamSphinx2022] and
quarto [@Allaire_Quarto_2022] for documentation.

>>>>

Bibat integrates many widely-adopted open-source tools to implement
the components of a Bayesian workflow. These include pydantic
[@pydanticdevelopersPydantic2022] and pandera [@niels_bantilan-proc-scipy-2020]
for data modelling, Stan [@carpenterStanProbabilisticProgramming2017]
for statistical inference, cmdstanpy [@standevelopmentteamCmdStanPy2022]
for python-Stan interface, arviz [@kumarArviZUnifiedLibrary2019]
for storing and analysing inferences, matplotlib [@Hunter:2007]
and lovelyplots [@sheriff_lovelyplots_2022] for plotting and sphinx
[@georgbrandlandthesphinxteamSphinx2022] and quarto [@Allaire_Quarto_2022] for
documentation.
